### 2017-11-06 1/exams/m2.tex
Tweaks.

\begin{center}
\begin{tabular}{| c | c |}
  \hline
  Question & Points \\ \hline \hline
  1 & 15 \\ \hline
  2 & 12 \\ \hline
  3 & 20 \\ \hline
  4 & 20 \\ \hline
  5 & 15 \\ \hline
  6 & 20 \\ \hline\hline
  Total: & 102\\
  \hline
\end{tabular}
\end{center}

@@

\begin{verbatim}
;; A Dict is one of:
;; - '()
;; - (cons (list String String) Dict)
;; Interp: represents a collection of definitions where each
;; element is a two-element list consisting of a word (first) and its
;; meaning (second).

@@

\newpage 
\noindent
{\bf Problem 4 (20 points).}
%
Here is a parametric data definition for a tree of elements:
\begin{verbatim}
;; A [Tree X] is one of:
;; - (make-leaf)
;; - (make-node X [Tree X] [Tree X])
;; Interp: a binary tree that is either empty (a leaf), or non-empty (a node)
;; with an element and two sub-trees.
(define-struct leaf ())
(define-struct node (elem left right))
\end{verbatim}
{\bf Problem 4(a) (10 points).} Design a function, {\tt tree-sum},
that operates on a binary tree of numbers, {\tt [Tree Number]}, and
produces the sum of all the numbers in the tree.

;; tree-sum : [Tree Number] -> Number
;; Sum all the numbers in the tree
(check-expect (tree-sum (make-leaf)) 0)
(check-expect (tree-sum (make-node 7 (make-node 1 (make-leaf) (make-leaf)) 
                                     (make-leaf)))
              8)
(define (tree-sum bt)
  (cond [(leaf? bt) 0]
        [(node? bt)
         (+ (node-elem bt)
            (tree-sum (node-left bt))
            (tree-sum (node-right bt)))]))

\noindent
{\bf Problem 4(b) (10 points).}
Here is a function that produces a list of all the elements in a tree:
\begin{verbatim}
;; tree-elems : [X] . [Tree X] -> [Listof X]
;; Produce a list of all elements in tree going top-down, left-to-right
(check-expect (tree-elems (make-leaf)) '())
(check-expect (tree-elems (make-node 7 
                                     (make-node 9 (make-leaf) (make-leaf))
                                     (make-node 2 (make-leaf) (make-leaf))))
              (list 7 9 2))
(define (tree-elems bt)
  (cond [(leaf? bt) '()]
        [(node? bt)
         (cons (node-elem bt)
               (append (tree-elems (node-left bt))
                       (tree-elems (node-right bt))))]))
\end{verbatim}
Here is an abstraction function for trees that is similar to
{\tt foldr} for lists, but works on trees:
\begin{verbatim}
;; tree-fold : [X Y] . [X Y Y -> Y] Y [Tree X] -> Y
;; The fundamental abstraction function for trees
(define (tree-fold f b bt)
  (cond [(leaf? bt) b]
        [(node? bt)
         (f (node-elem bt)
            (tree-fold f b (node-left bt))
            (tree-fold f b (node-right bt)))]))
\end{verbatim}
Give an equivalent definition of {\tt tree-elems} in terms of {\tt
  tree-fold}.  (Just provide the code.)

>>>>

\begin{center}
\begin{tabular}{| c | c |}
  \hline
  Question & Points \\ \hline \hline
  1 & 15 \\ \hline
  2 & 12 \\ \hline
  3 & 20 \\ \hline
  4 & 15 \\ \hline
  5 & 15 \\ \hline
  6 & 20 \\ \hline\hline
  Total: & 97\\
  \hline
\end{tabular}
\end{center}

@@

\begin{verbatim}
;; A Dict is one of:
;; - '()
;; - (cons (list String String) Dict)
;; Interp: a collection of definitions where each element is a 
;; two-element list of a word (first) and its meaning (second).

@@

\newpage 
\noindent
{\bf Problem 4 (15 points).}
%
Here is a parametric data definition for a tree of elements:
\begin{verbatim}
;; A [Tree X] is one of:
;; - (make-leaf)
;; - (make-node X [Tree X] [Tree X])
;; Interp: a binary tree that is either empty (a leaf), or non-empty (a node)
;; with an element and two sub-trees.
(define-struct leaf ())
(define-struct node (elem left right))
\end{verbatim}
%% {\bf Problem 4(a) (10 points).} Design a function, {\tt tree-sum},
%% that operates on a binary tree of numbers, {\tt [Tree Number]}, and
%% produces the sum of all the numbers in the tree.

%% \begin{SaveVerbatim}{VerbEnv}

%% SOLUTION:

%% ;; tree-sum : [Tree Number] -> Number
%% ;; Sum all the numbers in the tree
%% (check-expect (tree-sum (make-leaf)) 0)
%% (check-expect (tree-sum (make-node 7 (make-node 1 (make-leaf) (make-leaf)) 
%%                                      (make-leaf)))
%%               8)
%% (define (tree-sum bt)
%%   (cond [(leaf? bt) 0]
%%         [(node? bt)
%%          (+ (node-elem bt)
%%             (tree-sum (node-left bt))
%%             (tree-sum (node-right bt)))]))

%% \end{SaveVerbatim}

%% \censor{%
%% \noindent
%% \BUseVerbatim{VerbEnv}}

%% \newpage

\noindent
%{\bf Problem 4(b) (10 points).}
Here is a function that produces a list of all the elements in a tree:
\begin{verbatim}
;; tree-elems : [X] . [Tree X] -> [Listof X]
;; Produce a list of all elements in tree going top-down, left-to-right
(check-expect (tree-elems (make-leaf)) '())
(check-expect (tree-elems (make-node 7 
                                     (make-node 9 (make-leaf) (make-leaf))
                                     (make-node 2 (make-leaf) (make-leaf))))
              (list 7 9 2))
(define (tree-elems bt)
  (cond [(leaf? bt) '()]
        [(node? bt)
         (cons (node-elem bt)
               (append (tree-elems (node-left bt))
                       (tree-elems (node-right bt))))]))
\end{verbatim}
Here is an abstraction function for trees that is similar to
{\tt foldr} for lists, but works on trees:
\begin{verbatim}
;; tree-fold : [X Y] . [X Y Y -> Y] Y [Tree X] -> Y
;; The fundamental abstraction function for trees
(define (tree-fold f b bt)
  (cond [(leaf? bt) b]
        [(node? bt)
         (f (node-elem bt)
            (tree-fold f b (node-left bt))
            (tree-fold f b (node-right bt)))]))
\end{verbatim}
Give an equivalent definition of {\tt tree-elems} in terms of {\tt
  tree-fold}.  (Just provide the code.)
